%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% yale_thesis.tex
% Alexander Cerjan
% 2014/04/07
%
% A bare, sample template for a Yale PhD thesis using yalephd.cls
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,10pt]{yalephd}
% remove draft option for final printing.
% font size must be between 10pt-12pt.


\usepackage{soul}
\usepackage{enumitem}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{array}
\newcolumntype{L}{>{\centering\arraybackslash}m{2.5cm}}
\newcolumntype{K}{>{\centering\arraybackslash}m{2.2cm}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\usepackage{hhline}
%\usepackage{minted}
\usepackage{listings}
\PassOptionsToPackage{hyphens}{url}
\usepackage{longtable}
\usepackage[font=small,labelfont=bf]{caption}

\usepackage{booktabs}

\usepackage{xcolor} % to access the named colour LightGray
\definecolor{LightGray}{gray}{0.95}

\usepackage{geometry} % you need this for yalephd.cls to work.
\usepackage{graphicx} % you probably want the rest of these.
\graphicspath{{./}{hsc_morph/images/}{gamornet/images/}{gampen/images/}{morph_den/images/}{intro_and_conc/images/}}
\usepackage{dcolumn}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{wrapfig}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage{comment}
\usepackage{cite}
\usepackage{notoccite}
\usepackage{sectsty}
\usepackage[flushleft]{threeparttable}
\usepackage{pdflscape}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor = black, citecolor = blue}
\usepackage{xcolor}
\chapterfont{\Large\bfseries}
\sectionfont{\large\bfseries}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage{commands}
\usepackage{rotating}
\usepackage[most]{tcolorbox}
\usepackage{tikz}

\makeatletter
\newcommand{\DrawLine}{%
  \begin{tikzpicture}
  \path[use as bounding box] (0,0) -- (\linewidth,0);
  \draw[color=blue!75!black,dashed,dash phase=2pt]
        (0-\kvtcb@leftlower-\kvtcb@boxsep,0)--
        (\linewidth+\kvtcb@rightlower+\kvtcb@boxsep,0);
  \end{tikzpicture}%
  }
\makeatother



\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}


\usepackage{fontspec}
\newfontface{\bn}{kalpurush.ttf}


\newcommand\sersic{S\'ersic}
\newcommand\msun{$M_{\odot}$}
\newcommand\gamornet{G\textsc{a}M\textsc{or}N\textsc{et}}
\newcommand\gampen{GaMPEN}
\newcommand\lenstronomy{LENSTRONOMY}
\newcommand\grizy{\textit{grizy}}
\newcommand\uband{\textit{u}}
\newcommand\gb{\textit{g}}
\newcommand\rb{\textit{r}}
\newcommand\ib{\textit{i}}
\newcommand\zb{\textit{z}}
\newcommand\yb{\textit{y}}
\newcommand\om{\sim \mathcal{O}}


\begin{document}

% Need to define title before the abstract.
\title{Investigating Galaxy Morphology in Large Surveys Using Novel Machine Learning Frameworks} % capitalize the first letter in every word except conjunctions and prepositions
\author{\textbf{Aritra Ghosh} | \bn{অরিত্র ঘোষ}}
\advisor{Prof. C. M. Urry}
\date{December, 2023} % usually not \today.

% All the stuff at the front of your thesis.
\frontmatter

\begin{abstract}
The morphological features and structural parameters of galaxies serve as a cornerstone in comprehending their attributes and have played an instrumental role in our understanding of galaxy formation and evolution. In this work, we develop novel machine learning frameworks that can determine the morphology of billion-galaxy samples expected over the next decade. We demonstrate that our frameworks can be applied across a wide variety of ground and space-based datasets, can be trained with minuscule amounts of real data, and can predict $\sim15-60\%$ better uncertainties than existing morphology-determination tools.

We use our frameworks to create one of the largest structural parameter catalogs currently available, containing $\sim8$ million Hyper Suprime-Cam galaxies. This catalog represents a significant improvement in size ($\sim10\times$), depth ($\sim4$ mag), and uncertainty quantification over current state-of-the-art bulge+disk decomposition catalogs.  

We use this large sample to present one of the first comprehensive studies of the variation of galaxy radius with the environment – a relationship that has remained enigmatic with over a decade of conflicting results.  With $>5\sigma$ confidence, we confirm that galaxies in denser environments are $\sim10-20\%$ larger than equally massive counterparts in less dense regions of the Universe. We verify the presence of the above correlation separately for disk-dominated, bulge-dominated, star-forming, and quiescent sub-populations. We posit that the above correlation could be driven by assembly bias in dark matter halos and the varying prevalence of galaxy mergers in different environments.
\end{abstract}


\maketitle
\makecopyright{2024} % change as needed.
\tableofcontents
\listoffigures % remove this if you have no figures.
\listoftables % remove this if you have no tables.

\chapter{Acknowledgements} % this needs to be before \mainmatter.
I would like to express my deepest gratitude to the many individuals who have supported and inspired me throughout my journey towards this PhD thesis. Their contributions have been invaluable in shaping both my research and personal growth.

First and foremost, I am profoundly thankful to my advisor, Prof. Meg Urry, whose expertise, mentorship, and continuous support have been instrumental in shaping this thesis. Meg's deep insights, practical suggestions and constant encouragement allowed me to explore new horizons during my Ph.D., while still staying firmly focused on my ultimate goal. My time under Meg's guidance has made an indelible mark on my academic career, contributing immensely to my intellectual growth.

I extend my deepest appreciation to to Prof. Laurence Perreault Levasseur for being an excellent mentor, teacher, and collaborator. Various aspects of the machine learning frameworks developed in this thesis would not have been possible without Laurence's guidance and oversight. I am thankful to my esteemed collaborators and mentors -- Prof. Priyamvada Natarajan, Prof. Daisuke Nagai, Prof. Frank van den Bosch, Prof. David B Sanders, Dr. Kevin Schawinski. Their invaluable insights, constructive critiques, and collaborative spirit have played a pivotal role in shaping my research projects. 

I also wish to acknowledge the numerous discussions, brainstorming sessions, and camaraderie with fellow students at Yale and beyond that have made this academic journey enjoyable. Amrit Rau, Chuan Tian, Miles Cranmer, Zhengdong Wang, Kaustav Mitra, and Aayush Mishra warrant a special mention for their extended contributions to different aspects of this thesis. I must express my deepest gratitude to all the students, faculty, and staff members of Department of Astronomy at Yale University for providing a welcoming environment which made this research possible. My thesis also would not have been possible without the outstanding resources and staff members of the Yale Center for Research Computing. 

During my PhD, I had the privilege of contributing to and founding/leading dynamic groups and organizations, such as the Yale Astronomy Student Council, the Graduate Student Assembly, the Yale Graduate Housing Office, and the South Asian Graduate \& Professional Association at Yale. I would also like to extend my deepest gratitude to all my colleagues at these organizations for fostering a sense of community and making my time at Yale more fulfilling and meaningful. 

My heartfelt gratitude extends to my cherished friends, who have been my unwavering pillars of strength throughout this demanding academic journey. To  Uddipan Banik, Soham Jana, Sayoni Mitra, Mansa Srivastava, Dhruba Dutta Chowdhury, Satyanu Bhadra, Soham Mukhopadhyay, Souradeep Sengupta, Sharbatanu Chatterjee, Sunip Kumar Mukherjee, Dipanjana Roy, Preetha Sarkar, Kaustav Mitra, Tim Miller, Malena Rica, Yasmeen Asali, Imad Pasha, Juan Guerra, Zili Shen, Cheng-Han Hsieh, Julia Chin, and Gabriel Assumpcao --- thank you for cheering me on in times of triumph and offering kindness and support during the challenging moments. Your encouragement and camaraderie have not only lightened the academic load but have also enriched my life beyond measure.

I also had the great privilege of meeting my partner, Shivani Bhatt, during my time at Yale. Shivani's unwavering support has been a constant source of strength and inspiration,  crucial to the successful completion of my PhD. From acting as the first set of eyes on countless grant or job applications to excellent words of wisdom in moments of great difficulty --- I have leaned on her a great many times during this academic journey. Thank you for being my steadfast companion and for always believing in me --- your encouragement and shared moments of celebration have made this path more enjoyable.

I am grateful to my extended family --- especially Kaushambi Roy, Sourav Sarkar, and Souradip Roy --- for their constant love, generosity, kindness, and encouragement.  Last, but not the least, I owe an immeasurable debt of gratitude to my parents --- Nandita Ghosh, Somenath Ghosh --- and my aunt, Uma Ghosh. Their boundless love, constant encouragement, and unflagging support have been a beacon of light in difficult times and have provided the bedrock upon which I have built my academic pursuits. Their countless sacrifices, both seen and unseen, have allowed me to pursue my dreams with determination and focus. I dedicate this achievement to the dreams they have nurtured in me since the beginning. Their enduring faith in me has been the driving force behind this accomplishment, and I will forever carry their love and support with me in all my future endeavors.



% Starts proper arabic numbering of pages and chapters.
\mainmatter

\input{./intro_and_conc/intro}
\input{./gamornet/gamornet.tex}
\begin{subappendices}
    \input{./gamornet/gamornet_appendix.tex}
\end{subappendices}
\input{./gampen/gampen.tex}
\begin{subappendices}
    \input{./gampen/gampen_appendix.tex}
\end{subappendices}
\input{./hsc_morph/hsc_morph.tex}
\begin{subappendices}
    \input{./hsc_morph/hsc_morph_appendix.tex}
\end{subappendices}
\input{./morph_den/morph_den_2.tex}
\begin{subappendices}
     \input{./morph_den/morph_den_appendix_2.tex}
\end{subappendices}
\input{./intro_and_conc/conc}

\backmatter

\bibliographystyle{aasjournal}
\bibliography{./references}

\end{document}